\documentclass[margin,line,pifont,palatino,courier]{res}
\usepackage{url}
\usepackage[colorlinks,linkcolor=black,anchorcolor=black,citecolor=black]{hyperref}
\usepackage{pifont}
\usepackage[latin1] { inputenc}
\usepackage[scaled=0.92]{helvet}	% set Helvetica as the sans-serif font
\renewcommand{\rmdefault}{ptm}		% set Times as the default text font

% If AMS-LaTeX is used, it can be loaded before or after mtpro2
\usepackage{amsmath}		

% The following loads mtpro and defines some common MTPro options [2, 4]
%\usepackage[lite,subscriptcorrection,slantedGreek,nofontinfo]{mtpro2}


%\pdfmapfile{+mtpro2.map}
%\topmargin .5in
%\oddsidemargin -.5in
%\evensidemargin -.5in
%\textwidth=6.0in
 \textheight=9.0in
%\itemsep=0in
%\parsep=0in
\usepackage{fancyhdr}
%\topmargin=0in
%\textheight=8.5in
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
%\cfoot{\thepage}
%\lfoot{\textit{\footnotesize Research Statement}}
\rfoot{{\footnotesize Curriculum Vitae, Yujie Luo, \thepage}}


\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{\LARGE Yujie Luo \vspace*{.1in}}

\begin{resume}



\section{\sc Contact Information}

\vspace{.05in}
\begin{tabular}{@{}p{3.75in}p{2in}}
National University of Singapore  \\
Department of Mathematics            \\              
10 Lower Kent Ridge Road   \\               
Singapore 119076, Singapore    \\
Email: \texttt{lyj96@nus.edu.sg}\\
Personal webpage: \url{https://YujieLuo96.github.io/}\\
%Linkedin: \href{https://www.linkedin.com/in/yujie-luo-60837515b}{Yujie Luo}\\
\end{tabular}

\section{\sc Education}

{\bf  Johns Hopkins University}\\
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D.~in Mathematics, August 2018-May 2023.

\begin{list2}
\vspace*{.05in}
\item PhD Thesis: \href{https://jscholarship.library.jhu.edu/items/af3668a1-356b-4425-af17-4465dd465f84}{The minimal log discrepancy and its applications in birational geometry}
\item Advisor: Professor \href{https://web.math.princeton.edu/~chenyang/}{Chenyang Xu}, Co-Advisor: Professor \href{https://jingjunhan.github.io/}{Jingjun Han}.
\end{list2}
\end{list1}



{\bf University of Science and Technology of China (USTC)}\\
\vspace*{-.1in}
\begin{list1}
\item[] B. Sc.~in Mathematics, August 2014-June 2018.

\begin{list2}
\vspace*{.05in}
\item Undergrad Thesis: Dirichlet's problem for the complex Monge-Amp\`ere operator.
\item Advisor: Professor \href{http://www.math.ac.cn/hml/english/Academic2019/201903/t20190312_641152.html}{Xiangyu Zhou}.
\end{list2}

\end{list1}


\section{\sc Employment}

{\bf  National University of Singapore}\\
\vspace*{-.1in}
\begin{list1}
\item[] Peng Tsu Ann Assistant Professor (Visiting Fellow), August 2023-now.
\end{list1}


\section{\sc Research Interests}
Algebraic geometry, including birational geometry, algebraic dynamics, and the minimal model program.

\section{\sc Publications $\&$ Preprints}

\begin{list1}
\item \textit{Essential dimensions of polarized endomorphisms of certain algebraic surfaces} (joint with Qianli Fang and De-Qi Zhang). Preprint. [\href{https://arxiv.org/abs/2606.24103}{arxiv}]
\item \textit{Galois self-covers of projective spaces and essential dimensions} (joint with De-Qi Zhang). Preprint. [\href{https://arxiv.org/abs/2606.10207}{arxiv}]
\item \textit{Essential dimensions of polarized endomorphisms of abelian varieties} (joint with Keiji Oguiso and De-Qi Zhang). Preprint. [\href{https://arxiv.org/abs/2512.04942}{arxiv}]
\item \textit{Morphisms from a very general hypersurface} (joint with Yongnam Lee and De-Qi Zhang). \href{https://link.intlpress.com/JFirstDetail/1942307988947648514}{Pure Appl. Math. Q.} (special issue in honor of James McKernan's 60th birthday).
\item \textit{Jordan property for automorphism groups of compact varieties} (joint with Sheng Meng and De-Qi Zhang). \href{https://ems.press/journals/emss/articles/14298864}{EM Surv. Math. Sci.} (to appear).
\item \textit{ACC for minimal log discrepancies of terminal threefolds} (joint with Jingjun Han and Jihao Liu). \href{https://www.sciencedirect.com/science/article/abs/pii/S000187082500355X}{Adv. in Math.}, \textbf{480} (2025), Part A.
\item \textit{On boundedness of divisors computing minimal log discrepancies for surfaces} (joint with Jingjun Han). \href{https://www.cambridge.org/core/journals/journal-of-the-institute-of-mathematics-of-jussieu/article/on-boundedness-of-divisors-computing-minimal-log-discrepancies-for-surfaces/FD39003AD587E4711097363175E6F966}{J. Inst. Math. Jussieu}, \textbf{22}(6) (2023), 2907-2930.
\item \textit{Shokurov's conjecture on conic bundles with canonical singularities} (joint with Jingjun Han and Chen Jiang). \href{https://www.cambridge.org/core/journals/forum-of-mathematics-sigma/article/shokurovs-conjecture-on-conic-bundles-with-canonical-singularities/EC15D79B29D794C1637A2C80EC13DBA8}{Forum Math. Sigma}, \textbf{10}, E38.
\item \textit{Global ACC for foliated threefolds} (joint with Jihao Liu and Fanjun Meng). \href{https://www.ams.org/journals/tran/2023-376-12/S0002-9947-2023-09053-5/}{Trans. Amer. Math. Soc.}, \textbf{376}(12) (2023), 8939--8972.
\item \textit{A simple proof of ACC for MLD's for surfaces} (joint with Jingjun Han). \href{https://link.springer.com/article/10.1007/s10114-023-2094-x}{Acta Math. Sin. (Engl. Ser.)}, \textbf{40} (2024), 425--434.
\item \textit{Second largest accumulation point of minimal log discrepancies in dimension 3} (joint with Jihao Liu). Preprint, to appear in J. Pure. Appl. Algebra. [\href{https://arxiv.org/abs/2104.15072}{arxiv}]
\end{list1}

\section{\sc Invited Talks}
\begin{list2}
\item \emph{Essential dimensions of polarized endomorphisms II}, \href{https://www.math.sjtu.edu.cn/Default/seminarshow/tags/MDAwMDAwMDAwMLJ4hpaFyqF2}{Algebraic Geometry and Topology Seminar, Shanghai Jiao Tong University}, July 4, 2026.
\item \emph{Essential dimensions of polarized endomorphisms I}, \href{https://www.math.sjtu.edu.cn/Default/seminarshow/tags/MDAwMDAwMDAwMLJ4hpaFtKF2}{Algebraic Geometry and Topology Seminar, Shanghai Jiao Tong University}, July 3, 2026.
\item \emph{Essential dimensions of polarized endomorphisms of abelian varieties}, \href{https://www.math.nus.edu.sg/category/events/colloquia-seminars/topology-geometry-dynamics/}{Topology, Geometry and Dynamics Seminar, National University of Singapore}, June 30, 2026.
\item \emph{Essential dimensions of polarized endomorphisms of abelian varieties}, \href{https://sites.google.com/view/purduealgebraicgeometryseminar/home}{Purdue Algebraic Geometry Seminar}, January 21, 2026.
\item \emph{Essential dimensions of polarized endomorphisms of abelian varieties}, \href{https://scms.fudan.edu.cn/info/6223/11811.htm}{Shanghai Center for Mathematical Sciences}, January 8, 2026.
\item \emph{Essential dimensions of polarized endomorphisms of abelian varieties}, \href{https://math.ustc.edu.cn/2025/1222/c18702a717212/page.htm}{Algebraic Geometry Seminar ar USTC}, December 25, 2025.
\item \emph{Essential dimensions of polarized endomorphisms of abelian varieties}, \href{https://sites.google.com/ncts.ntu.edu.tw/2025-algebraic-geometry-in/2025-agea}{Algebraic Geometry in East Asia}, November 13, 2025.
\item \emph{Boundedness of divisors computing minimal log discrepancies and ACC conjecture for MLDs}, \href{http://events.kias.re.kr/h/AGEA23/?pageNo=4999}{Algebraic Geometry in East Asia}, November 9, 2023.
\item \emph{Shokurov's conjecture on conic bundles with canonical singularities}, \href{https://mathematics.jhu.edu/event/algebraic-geometry-seminar-yujie-luo-johns-hopkins/}{Algebraic Geometry seminar at Johns Hopkins University}, October 11, 2022.
\item \emph{ACC conjecture for minimal log discrepancies and its applications in birational geometry}, \href{https://faculty.wcas.northwestern.edu/yuchenl/AG_Seminar.html#yujie}{Algebraic Geometry seminar at Northwestern University}, October 5, 2022.
\item \emph{Second largest accumulation point of minimal log discrepancies of threefolds}, Short talks in \href{https://www.simonsfoundation.org/event/mps-conference-on-higher-dimensional-geometry-august-22-26-2022/}{MPS Conference on Higher Dimensional Geometry}, August 22-26, 2022.
\item \emph{Shokurov's conjecture on conic bundles with canonical singularities}, \href{http://staff.ustc.edu.cn/~yqliang/files/NTAG-1st.htm}{USTC NTAG 1-st}, April 13, 2021.
\item \emph{Shokurov's conjecture on conic bundles with canonical singularities}, \href{http://math.amss.cas.cn/xshd/xsbg/202101/t20210108_609547.html}{Morningside Center of Mathematics}, January 13, 2021.
\item \emph{On boundedness of divisors computing minimal log discrepancies for surfaces}, Short talks in \href{https://drive.google.com/file/d/1PuJ-Cmk3_-zPJLMf07lxQDFjc4as6bVJ/view}{Simons conference-Rationality}, July 30, 2020.
\item \emph{On boundedness of divisors computing minimal log discrepancies for surfaces}, Algebraic Geometry Seminar (Online), The University of Tokyo, July 26, 2020.
\end{list2}

\section{\sc Lectures and Seminar Talks}
\begin{list2}
\item \emph{Negative curves on $\mathbf{P}^2$ blowing up some points}, \href{https://www.math.nus.edu.sg/category/events/colloquia-seminars/topology-geometry-dynamics/page/9/}{National University of Singapore Geometry and Topology Seminar}.
\item \emph{Four lectures on the resolution of singularities}, \href{https://chenjiangfudan.github.io/home/2021-summer-reading.html}{Reading Workshop: Boundedness and Resolution at SCMS Fudan, 2021 summer}.
\item \emph{Princeton preprint seminar}, \href{https://web.math.princeton.edu/~le3339/preprint}{Logarithmic base change theorem and smooth descent of positivity of log canonical divisor }.
\end{list2}

\section{\sc Visitings}

{\bf  Graduate}

\begin{tabular}{@{}p{1.5in}p{7in}}
Nov 2023--Dec 2023& Department of Mathematics at East China Normal University\\
Jan 2022--Feb 2023& Department of Mathematics at Princeton University\\
May 2022--June 2023& Department of Mathematics at University of Utah\\
Jul 2021--Aug 2021& SCMS at Fudan University\\
Oct 2020--Jul 2021& BICMR at Peking University
\end{tabular}

{\bf  Undergraduate}

\begin{tabular}{@{}p{1.5in}p{7in}}
Oct 2017--May 2018 & Chinese Academy of Sciences\\
Jul 2017--Oct 2017& University of California, Los Angeles
\end{tabular}

\section{\sc Honors and Awards}

{\bf  University of Science and Technology of China}

\begin{tabular}{@{}p{1.5in}p{7in}}
2018 & Outstanding Undergraduates\\
2015 \& 2016 \& 2017& China National Scholarship\\
2017 & Prize of Hua Loo-Keng Talent Program in Mathematics\\
2015 \& 2016 \& 2017& Scholarship of of Hua Loo-Keng Talent Program
\end{tabular}


\section{\sc Teaching Experience}
{\bf  National University of Singapore}


\begin{tabular}{@{}p{1.5in}p{4in}}
2025 Spring & Instructor, Algebra I MA2202\\
2025 Spring & Instructor, Algebraic Geometry of Curves and Surfaces MA4273\\
2024 Spring \& Fall & Instructor, Multivariable Calculus MA2104\\
2023 Fall & Instructor, Algebraic Geometry MA5208 (Graduate Course)
\end{tabular}

{\bf  Johns Hopkins University}

\begin{tabular}{@{}p{1.5in}p{4in}}
2022 Summer & Teaching assistant, Calculus III \\
2020 Fall--2021 Fall & Teaching assistant, Linear Algebra \\
2020 Spring & Teaching assistant, Calculus II  \\
2019 Fall & Teaching assistant, Linear Algebra \\
\end{tabular}

{\bf  University of Science and Technology of China}

\begin{tabular}{@{}p{1.5in}p{4in}}
2017 Fall & Teaching assistant, Functional Analysis\\
\end{tabular}



%\section{\sc Graduate Courses}
%{\bf  Johns Hopkins University}

%\begin{tabular}{@{}p{5in}p{4in}}
%\begin{list1}
%\item Topics in Analysis: Blow-up of Euler's equation. (2020 Spring)
%\item Topics in PDEs: The Analysis of Black Holes. (2019 Fall)
%\item Topics in Mathematical Physics: Free-boundary Euler's equation. (2018 Fall)
%\item Topics in Mathematical Physics: General Relativity. (2018 Spring)
%\end{list1}
%\end{tabular}

%{\bf  University of Science and Technology of China}

%\begin{tabular}{@{}p{5in}p{4in}}
%\begin{list1}
%\item Nonlinear Dispersive PDEs (2017 Spring)
%\item PDEs of fluids: Inviscid Damping and Asymptotic Stability (2016 Fall)
%\item Graduate PDEs and Harmonic Analysis (2016 Spring)
%\item Topics in Stochastic Analysis (2016 Spring)
%\item Riemannian Geometry (2017 Spring)
%\end{list1}
%\end{tabular}


\end{resume}
\end{document}
